Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-02-09 Thesis/01-chap1.Rmd

**Artificial intelligence** (AI) is the field of research concerned with understanding and building machines who can demonstrate intelligence. As discussed in @russell_artificial_2002, historically, there are disagreements among researchers about the definition of intelligence, which is caused by two critical questions:

>>>>

**Artificial intelligence** (AI) is the field of research concerned with understanding and building machines who can demonstrate intelligence. As discussed in @russell_artificial_2002, historically, there are disagreements among researchers about the definition of intelligence, which is caused by two critical questions:
[ET: don't start with a definition as that makes the narrative dull. A lot of what you are writing definitions - which is relevant - but you want to interweave this as _narrative_. Why are you defining/describing these terms/disciplines? What's relevant and exciting?]
